\vskip-0.6in \Large Political Uncertainty

### 2016-02-03 GS-extension.tex
add obj fcn in terms of logit
add intuition on 0 to 1 to 2 to 3, further questions

@@

			The FOC wrt to $b\left(-\frac{1}{2}\right)$ is
					W_B \biggl[ \frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) - \\
					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr]  = 1
			Simplifying:
					W_B \frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \biggl[ \Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
					\left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) - 
					\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
					\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr]  = 1
			Simplifying further:
					\Phi\left(- \alpha + b(0) \right)+ \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
					- 2\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\right)^2}{2}} }
					\label{eq:firstfoc}

@@

\newpage
\subsection{Math for Discrete Model}
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Let
		\begin{enumerate}
			\item $X = -\alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
		\end{enumerate}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\[
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\begin{equation}
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		and
		\begin{equation}
			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
			\label{eq:base}
		\end{equation}
		Setting the left-hand size of these last two equations (the FOCs for the bribes for 0 and $\frac{1}{2}$ equal to each other,
		\[
		  \frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Y} + e^{-X-Z}}{1+e^{-X}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Y} + e^{-X-Z} + e^{-X-2Y} +e^{-X-Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-2X-Y} +e^{-X-Y-Z}
		\]
		\[
		  e^{-X-Z} +e^{-X-2Y}= e^{-Y-Z} +e^{-2X-Y}
		\]
		\[
		  e^{-Z} +e^{-2Y}= e^{X-Y-Z} +e^{-X-Y}
		\]
		\begin{equation}
		  e^{Y-Z} +e^{-Y}= e^{X-Z} +e^{-X}
			\label{eq:twoways}
		\end{equation}
   Equation~\ref{eq:twoways} can be rearranged into two similar forms. First:
		\[
		  e^{Y-Z} - e^{X-Z}= e^{-X} - e^{-Y}
		\]
		\begin{equation}
		  e^{Y} - e^{X}= e^Z\left(e^{-X} - e^{-Y}\right)
			\label{eq:1}
		\end{equation}
  	Second, multiplying through by zero:
	  \begin{equation}
		  e^{X} - e^{Y}= e^Z\left(e^{-Y} - e^{-X}\right)
			\label{eq:2}
		\end{equation}
	\end{itemize}	
In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(-\frac{1}{2}\right)$, we know that $Z < 0$. Note that this is due to the construction of the problem. This means $e^Z < 1$. In this case,
	\begin{itemize}
		\item Equation~\ref{eq:1} is consistent with $X>Y>0$, $X>0>Y$, or $0>X>Y$.
		\item Equation~\ref{eq:2} is consistent with $Y>X>0$, $Y>0>X$, or $0>Y>X$.
	\end{itemize}
The second order conditions will pin down the solution in this case of two non-negative bribes.

@@

>>>>

			Substituting from the definition of $X$ but substituting Logit for Probit and using the shorthand notation on the top of page~\pageref{page:sh},
					W_B \biggl[ \frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \left(1-\frac{1}{1+e^{-Y}}\right)  + \\
					\frac{1}{1+e^{-Z}} \left(1-\frac{1}{1+e^{-X}}\right) \frac{1}{1+e^{-Y}} + \\
					\left(1-\frac{1}{1+e^{-Z}} \right) \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} + \\
					\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)

@@

			The FOC wrt to $b\left(-\frac{1}{2}\right)$ is (in terms of probit)
				\begin{multline}
					W_B \biggl[ \frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) - \\
					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr]  = 1
				\end{multline}
			Simplifying:
			\begin{multline}
					W_B \frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \biggl[ \Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
					\left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) - 
					\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
					\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr]  = 1
				\end{multline}
			Simplifying further:
			  \begin{multline}
					\Phi\left(- \alpha + b(0) \right)+ \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
					- 2\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\right)^2}{2}} }
					\label{eq:firstfoc}
				\end{multline}

@@

\newpage
\subsection{Math for Discrete Model}
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Let
		\begin{enumerate}
			\item $X = -\alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\label{page:sh}$ 
		\end{enumerate}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\[
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\begin{equation}
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		and
		\begin{equation}
			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
			\label{eq:base}
		\end{equation}
		Setting the left-hand size of these last two equations (the FOCs for the bribes for 0 and $\frac{1}{2}$ equal to each other,
		\[
		  \frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Y} + e^{-X-Z}}{1+e^{-X}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Y} + e^{-X-Z} + e^{-X-2Y} +e^{-X-Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-2X-Y} +e^{-X-Y-Z}
		\]
		\[
		  e^{-X-Z} +e^{-X-2Y}= e^{-Y-Z} +e^{-2X-Y}
		\]
		\[
		  e^{-Z} +e^{-2Y}= e^{X-Y-Z} +e^{-X-Y}
		\]
		\begin{equation}
		  e^{Y-Z} +e^{-Y}= e^{X-Z} +e^{-X}
			\label{eq:twoways}
		\end{equation}
   Equation~\ref{eq:twoways} can be rearranged into two similar forms. First:
		\[
		  e^{Y-Z} - e^{X-Z}= e^{-X} - e^{-Y}
		\]
		\begin{equation}
		  e^{Y} - e^{X}= e^Z\left(e^{-X} - e^{-Y}\right)
			\label{eq:1}
		\end{equation}
  	Second, multiplying through by zero:
	  \begin{equation}
		  e^{X} - e^{Y}= e^Z\left(e^{-Y} - e^{-X}\right)
			\label{eq:2}
		\end{equation}
	\end{itemize}	
In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(-\frac{1}{2}\right)$, we know that $Z < 0$. Note that this is due to the construction of the problem. This means $e^Z < 1$. In this case,
	\begin{itemize}
		\item Equation~\ref{eq:1} is consistent with $X>Y>0$, $X>0>Y$, or $0>X>Y$.
		\item Equation~\ref{eq:2} is consistent with $Y>X>0$, $Y>0>X$, or $0>Y>X$.
	\end{itemize}
The second order conditions will pin down the solution in this case of two non-negative bribes.

@@

\vskip1in
The only intuition I see for why the next legislator is added in is that it's when the additional expense is justified by the increase in winning probability, conditional on the rule that 2+ legislators have to have the same gross ideal point
\begin{itemize}
	\item \textbf{What's the intuition for why they should be equal? Draw graph of the three PDFs in ideal point / net ideal point space}
	\item \textbf{Next question: How general is this result? That is, how much asymmetry can I have in the logistic distribution, $\beta$s, and for how broad a class of distributions would it hold? My conjecture is that it leans on having an interior single mode}
\end{itemize}
